---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.retina = 2
)

Sys.setenv(
  AWS_S3_STAGING_DIR = "s3://aws-athena-query-results-569593279821-us-east-1"
)

options(width=120)
```

# metis.jars

Amazon Athena JDBC Driver Wrapper Supporting the 'metis' Package

## Description

Contents of the Amazon Athena JDBC Driver 
<https://docs.aws.amazon.com/athena/latest/ug/connect-with-jdbc.html>
provided to support functions in the 'metis' package. Version number 
reflects the version number of the included 'JAR' file.

## IMPORTANT

Until a release of 'rJava' newer than '0.9.10' is on CRAN signals sent 
from interrupting Athena JDBC calls crash the R interpreter. You therefore 
need to set the `-Xrs` option to avoid signals being passed on to the JVM 
owner. That has to be done _before_ `rJava` is loaded so you either need 
to remember to put it at the top of all scripts _or_ stick this
in your local  `~/.Rprofile` and/or sitewide `Rprofile`:

```r
options(
  "java.parameters" = c(getOption("java.parameters", default = NULL), "-Xrs")
)
```
## What's Inside The Tin?

The following functions are implemented:

- `athena_supported_types`:	Retrieve the current supported type names in Athena
- `metis_jar_path()` : Retrieve the fully-qualified path to the included Athena JAR file
- `simba_driver_version`:	Retrieve the version of the Simba Athena JDBC driver included with the package

## Installation

```{r eval=FALSE}
devtools::install_git("https://git.sr.ht/~hrbrmstr/metis-jars")
# OR
devtools::install_gitlab("hrbrmstr/metis-jars")
# OR
devtools::install_github("hrbrmstr/metis-jars")
```

## Usage

```{r}
library(metis.jars)

# current verison
packageVersion("metis.jars")
```

```{r}
simba_driver_version()

athena_supported_types()

metis_jar_path()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
